---
title: "report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading, setting up

```{r}
library(tidyverse)
library(rtweet)
library(googlesheets4)
library(tidytags) # tidytags::process_tweets(searched_statuses)

d <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rlcFPlUgPMH-N30AMXNylSwUIl59qe5ECn7_kNaB53E/edit#gid=580742975")

# d <- read_csv(here('data', 'sample-of-tweets.csv'),
#               col_types = cols(
#                 id_str = col_character()
#               ))

d_level3 <- select(d, status_id = id_str, level3, created_at)

# searched_statuses <- tidytags::pull_tweet_data(id_vector = d_level3$status_id)
# 
# write_rds(searched_statuses, "searched-statuses.rds")

searched_statuses <- read_rds("searched-statuses.rds")

searched_statuses <- tidytags::process_tweets(searched_statuses)

users_data <- rtweet::users_data(searched_statuses) %>%
  distinct(user_id, .keep_all = T)

users_data %>%
  skimr::skim()
```

## Interactions

```{r}
dd <- searched_statuses %>%
  select(favorite_count, retweet_count, status_id) %>%
  left_join(d_level3)

interactions_table_back <- dd %>%
  group_by(level3) %>%
  mutate(total_interactions = favorite_count + retweet_count) %>%
  summarize(mean_fav = mean(favorite_count),
            sd_fav = sd(favorite_count),
            mean_rt = mean(retweet_count),
            sd_rt = sd(retweet_count),
            mean_total = mean(total_interactions),
            median_total = median(total_interactions),
            sd_total = sd(total_interactions)) %>%
  arrange(desc(mean_total))

interactions_table_back %>% 
  knitr::kable()

dd %>%
  group_by(level3) %>%
  mutate(total_interactions = favorite_count + retweet_count) %>%
  select(total_interactions) %>% 
  skimr::skim() %>% 
  knitr::kable()
```

## Time series

```{r}
ddd <- d_level3 %>%
  mutate(created_at = lubridate::ymd_hms(created_at)) %>%
  mutate(day = lubridate::round_date(created_at, unit = "day")) %>%
  mutate(day = day - lubridate::days(4)) %>% 
  mutate(week = lubridate::round_date(day, unit = "week")) %>%
  count(week, level3) %>%
  spread(level3, n, fill = 0) %>%
  gather(key, val, -week) %>%
  mutate(week_int = lubridate::week(week))
# mutate(val = ifelse(week == lubridate::ymd("2020-03-01"), val * (1 + 4/3), 
#                      ifelse(week == lubridate::ymd("2020-04-26"), val * (1 + 3/4),
#                              val)))

top_codes <- d %>%
  count(level3, sort = TRUE) %>%
  filter(n > 25) %>%
  rename(key = level3)

dddd <- ddd %>%
  semi_join(top_codes)

dddd
```

```{r}
dddd %>%
  ggplot(aes(x = week, y = val)) +
  geom_point(color = "darkgray") +
  geom_line() +
  facet_wrap(~key, scales = "free_y") +
  theme_minimal() +
  #geom_line() +
  scale_color_brewer(type = "qual") +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 13, family = "Times")) +
  theme(panel.grid.minor = element_blank()) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .8, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.")
```

# peaking around closures

remote learning, school closings, universal announcements, meals, requests, direct reply

```{r}
ggplot(subset(dddd, key %in% c("Direct Reply", "Remote Learning", "Meals", "Universal Announcements", "Requests", "School Closings")),
       aes(x = week, y = val, group = key, color = key)) +
  geom_point() +
  #geom_point(data = dddd, aes(x = week, y = val, group = key), color = "#DCDCDC") +
  #geom_line(data = dddd, aes(x = week, y = val, group = key), color = "#DCDCDC") +
  geom_line() +
  # facet_wrap(~key, scales = "free_y") +
  theme_bw() +
  #geom_line() +
  scale_color_brewer("", type = "qual") +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 15, family = "Times")) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .7, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.") +
  ylim(0, 35) +
  labs(subtitle = "Peaking in Frequency Around School Closures")

ggsave("pattern-1.png", width = 10, height = 7)
```


# peaking later

spreading positive messages, staff highlight, student highlight, community highlight, health resources, events

```{r}
ggplot(subset(dddd, key %in% c("Spreading Positive Messages", "Staff Highlight", "Student Highlight", "Community Highlight", "Helath Resources", "Events")),
       aes(x = week, y = val, group = key, color = key)) +
  geom_point() +
  #geom_point(data = dddd, aes(x = week, y = val, group = key), color = "#DCDCDC") +
  #geom_line(data = dddd, aes(x = week, y = val, group = key), color = "#DCDCDC") +
  geom_line() +
  # facet_wrap(~key, scales = "free_y") +
  theme_bw() +
  #geom_line() +
  scale_color_brewer("", type = "qual", palette = 2) +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 15, family = "Times")) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .7, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.") +
  ylim(0, 35) +
  labs(subtitle = "Peaking in Frequency Following Closures")

ggsave("pattern-2.png", width = 10, height = 7)
```

# declining after beginning frequent

unrelated to COVID

```{r}
ggplot(subset(dddd, key %in% c("Unrelated to COVID")),
       aes(x = week, y = val, group = key, color = key)) +
  geom_point() +
  #geom_point(data = dddd, aes(x = week, y = val, group = key), color = "#DCDCDC") +
  #geom_line(data = dddd, aes(x = week, y = val, group = key), color = "#DCDCDC") +
  geom_line() +
  # facet_wrap(~key, scales = "free_y") +
  theme_bw() +
  #geom_line() +
  scale_color_brewer("", type = "qual", palette = 3) +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 15, family = "Times")) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .7, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.") +
  labs(subtitle = "Declining in Frequency Following Closures")

ggsave("pattern-3.png", width = 10, height = 7)
```

all of this may not be that helpful

```{r}
dddb <- d_level3 %>%
  mutate(created_at = lubridate::ymd_hms(created_at)) %>%
  mutate(week = lubridate::round_date(created_at, unit = "week")) %>%
  count(week, level3) %>%
  spread(level3, n, fill = 0) %>%
  gather(key, val, -week) %>%
  mutate(week_int = lubridate::week(week))

ddddb <- dddb %>%
  semi_join(top_codes)

small_plot <- dddd %>% 
  group_by(week) %>% 
  summarize(sum_val = sum(val))

small_plot
```

```{r}
f <- function(data) {
  glm(val ~ week_int, data = data, family = "poisson")
}

ff <- function(data) {
  glm(val ~ week_int + I(week_int^2), data = data, family = "poisson")
}

my_order <- top_codes %>% arrange(key)

my_order <- my_order %>%
  mutate(order = 1:10)

l <- dddd %>%
  arrange(key) %>%
  group_by(key) %>%
  group_split() %>%
  purrr::map(f)

res_tab <- dddd %>%
  arrange(key) %>%
  group_by(key) %>%
  group_split() %>%
  purrr::map(f) %>%
  map_df(broom::tidy) %>%
  mutate(order = rep(1:10, each = 2)) %>%
  left_join(my_order) %>%
  filter(term == "week_int") %>%
  mutate(p.value = round(p.value, 3)) %>%
  arrange(desc(abs(estimate)))

res_tab <- res_tab %>%
  mutate(pattern = c(
    "decrease",
    rep("increase", 4),
    rep("unchanged", 5)
  ))

ddddb <- left_join(ddddb, res_tab)
```

quadratic

```{r}
li <- dddd %>%
  arrange(key) %>%
  group_by(key) %>%
  group_split() %>%
  purrr::map(ff)

res_tabi <- dddd %>%
  arrange(key) %>%
  group_by(key) %>%
  group_split() %>%
  purrr::map(ff) %>%
  map_df(broom::tidy) %>%
  mutate(order = rep(1:10, each = 3)) %>%
  left_join(my_order) %>%
  filter(str_detect(term, "week_int")) %>%
  mutate(p.value = round(p.value, 3)) %>%
  arrange(desc(abs(estimate)))

res_tabi <- res_tabi %>%
  mutate(pattern = c(
    "decrease"
    # rep("increase", 4),
    # rep("unchanged", 5)
  ))

ddddi <- left_join(dddd, res_tabi)

res_tabi
```

## decrease

- unrelated to COVID 

## increase

- student highlight
- staff highlight
- events 
- spreading positive messages

# unchanged

- school closings
- health resources 
- remote learning 
- meals
- universal announcement

````{r}
dddd %>%
  ggplot(aes(x = week, y = val)) +
  geom_point(color = "darkgray") +
  geom_line() +
  facet_wrap(~key, scales = "free_y") +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1)
```

```{r}
dddd %>%
  left_join(res_tab) %>% 
  mutate(key = fct_reorder(key, val, sum, .desc = TRUE)) %>% 
  filter(pattern == "decrease") %>% 
  ggplot(aes(x = week, y = val)) +
  geom_point(color = "darkgray") +
  geom_line() +
  # geom_line(data = subset(ddddb, pattern == "increase"), aes(x = week, y = val, group = key)) +
  #geom_smooth(method = "lm", se = F, color = "black") +
  #geom_col(data = small_plot, aes(x = week, y = sum_val), fill = 'lightgray') +
  # geom_line(color = "darkblue", alpha = .5) +
  theme_minimal() +
  #geom_line() +
  scale_color_brewer(type = "qual") +
  facet_wrap(~key, ncol = 3) +
  # facet_grid(rows = vars(pattern), cols = vars(key)) +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 13, family = "Times")) +
  # theme(panel.grid.major = element_line(colour = "lightgray"))
  theme(panel.grid.minor = element_blank()) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .8, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.")

ggsave("posts-over-time-increase.png", width = 10, height = 6)

dddb %>%
  left_join(res_tab) %>% 
  mutate(key = fct_reorder(key, val, sum, .desc = TRUE)) %>% 
  filter(pattern == "unchanged") %>% 
  ggplot(aes(x = week, y = val)) +
  geom_point(color = "darkgray") +
  geom_line() +
  # geom_line(data = subset(ddddb, pattern == "increase"), aes(x = week, y = val, group = key)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  #geom_col(data = small_plot, aes(x = week, y = sum_val), fill = 'lightgray') +
  # geom_line(color = "darkblue", alpha = .5) +
  theme_minimal() +
  #geom_line() +
  scale_color_brewer(type = "qual") +
  facet_wrap(~key, ncol = 3) +
  # facet_grid(rows = vars(pattern), cols = vars(key)) +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 13, family = "Times")) +
  # theme(panel.grid.major = element_line(colour = "lightgray"))
  theme(panel.grid.minor = element_blank()) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .8, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.")

ggsave("posts-over-time-unchanged.png", width = 10, height = 6)

dddb %>%
  left_join(res_tab) %>% 
  mutate(key = fct_reorder(key, val, sum, .desc = TRUE)) %>% 
  filter(pattern == "decrease") %>% 
  ggplot(aes(x = week, y = val)) +
  geom_point(color = "darkgray") +
  geom_line() +
  # geom_line(data = subset(ddddb, pattern == "increase"), aes(x = week, y = val, group = key)) +
  geom_smooth(method = "lm", se = F, color = "black") +
  #geom_col(data = small_plot, aes(x = week, y = sum_val), fill = 'lightgray') +
  # geom_line(color = "darkblue", alpha = .5) +
  theme_minimal() +
  #geom_line() +
  scale_color_brewer(type = "qual") +
  facet_wrap(~key, ncol = 3) +
  # facet_grid(rows = vars(pattern), cols = vars(key)) +
  ylab("Number of Posts") +
  xlab(NULL) +
  theme(text = element_text(size = 13, family = "Times")) +
  # theme(panel.grid.major = element_line(colour = "lightgray"))
  theme(panel.grid.minor = element_blank()) +
  scale_x_datetime(labels = scales::date_format("%m-%d")) +
  geom_vline(xintercept = lubridate::ymd_hms("2020-03-17 00:00:00"), alpha = .8, linetype = "dashed") +
  labs(caption = "Note. Dashed line indicates the mean date on which districts closed.")

ggsave("posts-over-time-decrease.png", width = 5, height = 3)
```
